---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README_files/README-"
)
```

# Introduction

This package facilitates the use of the official ERCOT palette with `ggplot2` plots.

## Installation

You can install this package from GitHub by calling `devtools::install_github("aelhabr/ercotr")`.

## Notes

Note the global variables that are loaded into your environment when loading this package.
These include:

- `ercot_palette`
- `ercot_palette2`
- `ercot_palette_w_contrast` (alias to `ercot_palette`)
- `ercot_palette_wo_contrast` (alias to `ercot_palette2`)

These variables are used in the `scale_color/fill_ercot()`
and `scale_color/fill_ercot2()` functions respectively.

The `2` variation implement the ordering of the actual official ERCOT palette
(i.e. turquoise first, grey second, light green third, etc.)
while the un-suffixed counterparts reflect a subjective re-ordering
of the same colors that (arguably) improve the contrast in plots.
(For example, maroon is the second color instead of grey in the non-suffixed
palette because it (arbuably) contrasts better with the 
first color, turquoise.) Please feel free to use either of these built-in palettes,
or to re-order the colors to your liking (e.g. by calling `ercot_palette[c(1, 8, 6)]`, etc.).

In general, it is recommended to only use the `scale_color/fill_ercot()` and
`scale_color/fill_ercot2()` functions directly.
(Correspodningly, it is not recommended to use other available functions,
such as`ercot_pal()` and `ercot_pal2()`, directly. 
Note that these functions exist primarily to serve as analogues to t
he `ggplot2` `manual_pal()` function.)

## Examples

These examples are very similar shown in the `README` file for the `teutils` package.

```{r }
library("ggplot2")
library("ercotr")

viz_labs <-
    labs(title = "A Title.",
       subtitle = "A subtitle.",
       caption = "A caption.")

viz_cars <-
  ggplot(mtcars, aes(x = wt, y = mpg, color = factor(gear))) +
  geom_point(size = 2) +
  geom_smooth(method = "lm", se = FALSE, size = 2) +
  viz_labs

viz_cars_facet <-
  viz_cars +
  facet_wrap(~ am)

viz_diamonds <-
  ggplot(diamonds, aes(x = clarity, fill = cut)) +
  geom_bar() +
  viz_labs

viz_cars + theme_grey()
viz_cars + scale_color_ercot() + theme_minimal()

viz_cars_facet + theme_grey()
viz_cars_facet + scale_color_ercot() + theme_minimal()

viz_diamonds + scale_fill_ercot() + theme_minimal()
viz_diamonds + scale_fill_ercot2() + theme_minimal()
```


